\begin{recipe}{Eggplant Rolls~(Involtini)}{Nonna}{}

\begin{ingredients}
\item 3~medium \theme{eggplant} or 6~large \theme{zucchini}
\item \seerecipe{PastaSauce:PlainTomatoSauce} diluted with water
\item 3~eggs
\item all-purpose flour
\item oil
\item cooked ham, cut in \inch{2} strips
\item \htheme{Parmesan}{cheese}, grated
\item \htheme{mozzarella}{cheese}, cut in long \inch{\quarter}$\times$\inch{\quarter} rectangles
\end{ingredients}

\begin{directions}
\item Peel eggplant and slice \inch{\quarter} thick.
\item Salt and lay in colander.
\item Cover with a plate and place a weight on top.
\item Allow to drain at least \half{}~hour.
\item Rinse and squeeze dry.
\item In a bowl, beat eggs and \C{\half} water.
\item Dredge eggplant in flour, then eggs.
\item Fry slowly in \inch{1} oil until golden on both sides.
\item Drain fried slices in colander until cool enough to handle.
\item Preheat oven to \tF{375}.
\item In a casserole dish, spread a thin layer of sauce.
\item Layout eggplant slices.
\item On each eggplant slice, spread a thin layer of sauce, sprinkle with Parmesan, and lay on a piece of ham.
\item Place a piece of mozzarella at the small end.
\item Roll eggplant tightly starting at the small end and place in row in the casserole dish.
\item Once pan is full, sprinkle with Parmesan and add a thin layer of sauce.
\item Bake, uncovered, for 15 to 20~minutes until liquid is absorbed and surface is slightly crusted.
\item Cover and let rest at least 10~minutes before serving.
\end{directions}

\hint{Do not attempt to put two layers of rolls in a casserole.}
\hint{Can be allowed to stand for a long time before serving.}
\end{recipe}
