\begin{recipe}{Party Paella}{Heather}{4 to 6~servings}

\begin{ingredients}
\item 1~medium red \theme{bell pepper}
\item \C{\quarter} olive oil
\item \lbs{\half} \theme{chicken} breast, cut into \inch{1} pieces
\item \lbs{\half} \theme{shrimp}, peeled and deveined
\item 1~large onion, chopped
\item 2~cloves of garlic, finely chopped
\item 2~large plum tomatoes, chopped
\item \lbs{\quarter} chorizo sausage or smoked ham, chopped
\item \tp{\half} hot pepper flakes
\item \C{1\half} Spanish short-grain \theme{rice}
\item \C{\half} dry white wine
\item \C{3} chicken stock
\item \tp{\quarter} saffron
\item \tp{\half} salt
\item \tp{\quarter} pepper
\item \lbs{\half} \shtheme{halibut}{fish} or other white fish fillet, skinned and cut into \inch{1} pieces
\item 6~\theme{mussels}
\item 6~\theme{clams}
\item \C{1} green \theme{peas}
\end{ingredients}

\begin{directions}
\item Preheat oven to \tF{500}.
\item Bake pepper until charred. Approximately 20~minutes.
\item Place in a covered bowl and let cool.
\item Preheat oven to \tF{400}.
\item Heat \Tp{2} oil in a paella pan or large skillet over high heat.
\item Lightly brown chicken. Approximately 4~minutes.
\item Remove chicken and set aside.
\item Cook shrimp until just pink. Approximately 3~minutes.
\item Remove shrimp and place with chicken.
\item Reduce heat to medium.
\item Sauté onion and garlic. Approximately 4~minutes.
\item Add tomatoes, sausage, and pepper flakes.
\item Cook until dry. Approximately 6~minutes.
\item Add rice and cook 1~minute.
\item Stir in wine.
\item Stir in stock, saffron, salt, and pepper.
\item Bring to a boil.
\item Simmer 15~minutes.
\item Peel charred skin from the pepper and remove the core and seeds.
\item Cut the pepper into thin strips.
\item Stir chicken, shrimp, and fish into rice mixture.
\item Nestle mussels and clams into rice with open edges facing up.
\item Sprinkle red pepper strips and peas in between.
\item Bake until rice is tender and mixture is almost dry. Approximately 15~minutes.
\item Remove from oven and cover.
\item Let stand 10~minutes.
\end{directions}

\hint{}
\end{recipe}
