\begin{recipe}{German Chocolate-Hazelnut Wafers}{}{3 dozen}

\begin{ingredients}
\item \C{1} toasted, skinned hazelnuts or toasted almonds (see bottom)
\item \C{\third} sugar
\item \oz{4} bittersweet chocolate, roughly chopped
\item \C{\half} unsalted butter, at room temperature
\item \tp{1} vanilla extract
\item \tp{2} Frangelico or Amaretto
\item 2 eggs yolks
\item \C{1} all-purpose flour
\end{ingredients}

\begin{directions}
\item In a food processor or blender, combine the nuts and \Tp{1} of the sugar and grind finely.
\item Trasfer to a bowl.
\item Place chocolate in the same applicance and process until finely shredded.
\item Add to the bowl holding the nuts.
\item In a bowl, using an electric mixer or a spoon, cream together the butter and the remaining sugar until light.
\item Beat in the vanilla, liqueur, and egg yolks until well mixed.
\item Add the flour and the reserved nuts and chocolate and mix until blended.
\item Scrape out onto a sheet of plastic wrap and, using the wrap, not your fingers, shape into a log about \inch{2\quarter} in diameter.
\item Wrap and chill for 1~hour, or until firm.
\item Preheat the oven to \tF{325}.
\item Lightly grease baking sheets, or use nonstick baking sheets.
\item Slice the log into rounds \cm{\half} thick.
\item Place on the prepared baking sheets, spacing them about \cm{1\half} apart.
\item Bake the cookies for 10 to 12~minutes, or until light brown on edges.
\end{directions}

\hint{Store the cookies in an airtight container for up to 10~days.}
\end{recipe}
