\begin{recipe}{Snickerdoodles}{Andre Masella}{}


\begin{ingredients}
\item \gr{230} unsalted butter
\item \gr{267} granulated sugar
\item 1~large egg, at room temperature
\item \gr{375} all-purpose flour
\item \tp{2} cream of tartar
\item \tp{1} baking soda
\item \tp{1\half} ground cinnamon
\item \tp{\half} salt
\item \tp{2} vanilla extract
\end{ingredients}

Topping
\begin{ingredients}
\item \gr{40} toasted sugar
\item \tp{\half} ground cinnamon
\item \tp{\quarter} salt
\end{ingredients}

\begin{directions}
\item Heat butter in a saucepan over medium low heat until milk solids fall to bottom of pan.
\item Filter butter using a coffee filter to remove solids. Transfer to a new pan.
\item Continue to heat butter until dark amber.
\item Allow butter to cool until solid.
\item Cream sugar and butter until well combined.
\item Add eggs and beat until gritty.
\item Separately, combine dry ingredients.
\item Add dry ingredients to creamed mixture.
\item Add vanilla extract.
\item Roll into balls; if mixutre is too crumbly to form, chill approximately 20~minutes.
\item Cover and chill overnight.
\item Remove balls from fridge and lest rest for 30~minutes.
\item Preheat oven to \tF{375}.
\item Combine topping ingredients in a blender. Briefly pulse to make sugar and salt crystals uniform.
\item Mist balls with water and allow to stand until tacky but not wet.
\item Roll balls in topping mixture and arrange on sheet pans.
\item Bake for 10~minutes.
\item Cool on the pan for 5~minutes.
\item Transfer to a wire rack and cool completely.
\end{directions}
\method{Creaming}
\end{recipe}
