\begin{recipe}{Gnocchi di Patate}{Nonna}{}

\begin{ingredients}
\item (\gr{56} $+$ \gr{50}) per person all-purpose flour
\item \gr{100} per person Yukon Gold \theme{potato}es\footnote{This is the weight after ricing.}
\item \gr{8} per person egg (\eighth{} of an egg)
\end{ingredients}

\begin{directions}
\item Boil unpeeled potatoes in unsalted water until fork tender.
\item Rice potatoes and discard skins.
\item Let potatoes cool.
\item Sift flour on to a work surface, in two piles.
\item Make a well with the \gr{56} pile.
\item Put potatoes in well.
\item Crack egg in centre of potatoes.
\item Mix egg into potatoes.
\item Incorporate flour into potatoes.
\item Knead until a rough dough forms, scraping bench.
\item Set dough aside and working in batches.
\item Heavily flour surface with remaining flour.
\item Knead a piece of dough until just smooth (i.e., the dough does not tear or crack when worked). Keep the work surface floured.
\item On a heavily floured surface, roll in ropes \inch{\threequarter} diameter.
\item Cut ropes into pillows \inch{1} long.
\item Shape into gnocchi using a floured grooved gnocchi board or fork. To shape:\par
\begin{enumerate*}
\item Using two to three floured fingers, press a pillow near the bottom edge of the board starting just above the bottom edge of the pillow.
\item Drag the pillow toward the top of the board, maintaining constant distance from the board. This does not require any pressure.
\item When the pillow has been almost completely dragged, release it.
\end{enumerate*}
\item If desired, lay out on a floured cookie sheet, freeze for \half{}~hour, then dump in a bag, and return to freezer. Cook without defrosting.
\item Boil in salted water for 5 to 7~minutes. For large quantities, cook small batches.
\end{directions}

\hint{The potatoes must be boiled in their skins to prevent excess water absorption.}
\hint{Do not let finished pasta sit more than 1\half{}~hours before boiling. It is better to freeze them or at least refrigerate them.}
\hint{Ensure that all surfaces and the gnocchi are well-floured.}
\end{recipe}
