\begin{recipe}{Maccarunë a fiérrë}{Nonna}{}

\begin{ingredients}
\item \gr{100} fine semolina flour per person, or \gr{50} each coarse semolina and all-purpose flour
\item \gr{53} hot tap water per person
\end{ingredients}

\begin{directions}
\item Sift flour.
\item Make a well and add water.
\item Knead until dough just comes together.
\item Divide dough into pieces.
\item Knead by folding the piece and rolling in to a rope repeatedly until it is smooth.
\item Roll out the rope until it is \inch{\quarter} thick.
\item Divide into \inch{6} lengths.
\item Dust with flour.
\item Shape ropes into maccarunë. To shape:\par
\begin{enumerate*}
\item Place the rod at an angle to the dough so the right tip of the rope meets the rod a few inches from the right end of the rod.
\item Hold the left end of the rod between the thumb and forefinger.
\item Using the base of the right thumb, roll the dough into the rod applying light pressure at the point of winding. The coils should just touch.
\item Periodically, use the left hand to move the rod back to the starting position.
\item With light pressure, roll the rod back and forth with the heels of the hands on the dough. This will thin dough.
\item Cradle the dough with the left hand holding the rod with the thumb and forefinger just beyond the right edge of the dough.
\item Use the right hand to remove the rod, releasing the dough.
\end{enumerate*}
\item Allow pasta to dry for at least \half{}~hour.
\item Cook in boiling, salted water until tender.
\end{directions}

\hint{The rod, the fiérrë, is a \inch{12}-long piece of \inch{\sfrac{1}{16}} key stock. Key stock can be purchased from most industrial fastener vendors. I found it at \href{http://www.spaenaur.com/}{Spaenaur} in Kitchener as part number~131-450.}
\hint{This process can be made easier by flattening the dough in a pasta maker and, slicing it into wide strips, and then rolling the strips on to the fiérrë. This is much faster and produces much more even pieces of pasta, but they are more likely to uncurl.}
\end{recipe}
