\begin{recipe}{Chocolate-Pecan Caramel Candy Bars}{}{about 40}

\subrecipe{Crust}

\begin{ingredients}
\item \C{1 \half} all-purpose flour
\item \C{\half} firmly packed light brown sugar
\item \C{\half} chilled unsalted butter
\end{ingredients}

\begin{directions}
\item Preheat the oven to \tF{350}.
\item Line a \inch{9}$\times$\inch{13} baking pan with aluminium foil and grease the foil.
\item In a food processor or in a bowl, combine the flour and sugar and pulse briefly or stir to mix.
\item Add the butter and process or mix until crumbly.
\item Transfer to the prepared pan and pat evenly onto the bottom of the pan.
\item Bake for 12~minutes.
\item Transfer the pan to a rack.
\end{directions}

\subrecipe{Topping}

\begin{ingredients}
\item \Tp{6} unsalted butter, at room temperature
\item \C{1} firmly packed dark brown sugar
\item \Tp{3} honey
\item \Tp{3} heavy cream
\item \Tp{2} maple syrup
\item \C{1 \half} chopped \theme{pecans} or \theme{walnuts}
\item \C{\half} semisweet chocolate chips
\end{ingredients}

\begin{directions}
\item In a saucepan, heat the butter over low heat until it melts and bubbles.
\item Add the brown sugar, honey, cream, and maple syrup and bring to a boil over medium heat, stirring constantly.
\item Let boil without stirring for 1~minute.
\item Pour over the hot crust and sprinkle evenly with the nuts.
\item Return the pan to the oven and bake for 12 to 15~minutes, or until caramel layer is bubbly.
\item Remove from the oven and sprinkle with the chocolate chips.
\item Let melt for 1 to 2~minutes, then swirl with a spatula.
\item Let cool.
\item Invert the baked sheet onto a rack, lift off the pan, and peel off the foil.
\item Cut into bars.
\end{directions}

\hint{Store the bars between sheets of waxed paper in an airtight container for up to 1~week.}
\end{recipe}
