\begin{recipe}{Croissants\UNTESTED}{}{}

\begin{ingredients}
\item \tp{1\quarter} dry yeast
\item \Tp{3} warm water (\tC{45})
\item \tp{1} sugar
\item \C{1\threequarter} all-purpose flour
\item \tp{2} sugar
\item \tp{1\half} salt
\item \C{\twothird} warm milk
\item \Tp{2} oil
\item \C{\twothird} unsalted butter, chilled
\item 1~egg
\item \Tp{1} water
\end{ingredients}

\begin{directions}
\item Combine yeast, warm water, and \tp{1} sugar. Allow to stand until creamy and frothy.
\item Measure flour into a mixing bowl.
\item Dissolve \tp{2} sugar and salt in warm milk.
\item Blend into flour along with yeast and oil.
\item Mix well; knead until smooth.
\item Cover, and let rise until over triple in volume.
\item Deflate gently, and let rise again until doubled. Deflate and chill 20~minutes.
\item Massage butter until pliable, but not soft and oily.
\item Pat dough into a \cm{35}$\times$\cm{20} rectangle.
\item Smear butter over top two thirds, leaving \cm{\half} margin all around.
\item Fold unbuttered third over middle third, and buttered top third down over that.
\item Turn \ang{90}, so that folds are to left and right.
\item Roll out to a \cm{35}$\times$\cm{15} rectangle.
\item Fold in three again.
\item Sprinkle lightly with flour, and put dough in a plastic bag.
\item Refrigerate 2~hours.
\item Unwrap, sprinkle with flour, and deflate gently.
\item Roll to a \cm{35}$\times$\cm{15} rectangle, and fold again.
\item Turn \ang{90}, and repeat.
\item Wrap, and chill 2~hours.
\item To shape, roll dough out to a \cm{50}$\times$\cm{13} rectangle.
\item Cut in half crosswise, and chill half while shaping the other half.
\item Roll out to a \cm{40}$\times$\cm{12} rectangle.
\item Cut into three \cm{12} squares.
\item Cut each square in half diagonally.
\item Roll each triangle lightly to elongate the point, and make it \cm{18} long.
\item Grab the other 2 points, and stretch them out slightly as you roll it up.
\item Place on a baking sheet, curving slightly.
\item Let shaped croissants rise until puffy and light.
\item In a small bowl, beat together egg and \Tp{1} water.
\item Glaze croissants with egg wash.
\item Bake in a preheated \tF{475} oven for 12 to 15~minutes.
\end{directions}
\end{recipe}
