\begin{recipe}{Easter Babka}{Ukrainian Daughter's Cookbook}{4 to 6~loaves}

\begin{ingredients}
\item \Tp{2} instant yeast
\item \C{\third} water, lukewarm
\item \tp{1} sugar
\item \C{1} milk
\item \C{\half} butter
\item 8~egg yolks
\item 2~egg whites
\item \C{1} sugar
\item \C{\half} orange juice
\item zest of 1~orange
\item zest of 1~lemon
\item \tp{1} vanilla
\item \tp{1} salt
\item \C{6} flour
\item \C{\half} \theme{raisins}
\item egg wash
\end{ingredients}

\begin{directions}
\item Combine yeast, lukewarm water, and \tp{1} sugar.
\item Bring milk to a boil.
\item Add butter and let cool.
\item Beat egg yolks and egg whites until light.
\item Beat in sugar.
\item Add egg mixture to milk mixture.
\item Stir in juice, zests, vanilla, salt.
\item Add risen yeast mixture.
\item Toss raisins in a small amount of flour.
\item Mix in flour and raisins to batter.
\item Knead until smooth and elastic.
\item Let rise until doubled in size.
\item Knead briefly.
\item Let rise until doubled in size.
\item Divide dough.
\item Form into a ball \third~the size of the pan.
\item Let rise until tripled.
\item Preheat oven to \tF{350}.
\item Glaze with egg wash.
\item Bake until browned on the bottom and sound hollow when tapped. Approximately 30~minutes, but this will vary strongly with size and rise time.
\end{directions}

\hint{Large coffee cans or small soup cans are the preferred pan to produce the traditional ``mushroom''-shaped loaves.}
\hint{Breads freeze quite well.}
\hint{Traditionally, this is served for Easter Monday breakfast with eggs and kielbasa.}
\end{recipe}
