\begin{recipe}{Hot Cross Buns}{Canadian Living}{9~buns}

\begin{ingredients}
\item \C{\quarter} lukewarm water
\item \C{\half} sugar
\item 1~package dry yeast
\item \C{3\half} all-purpose flour
\item \Tp{2} cinnamon
\item \tp{1} nutmeg
\item \tp{\half} salt
\item \tp{\quarter} cloves
\item \C{\threequarter} milk, warm
\item \C{\quarter} butter, melted
\item 1~egg
\item 1~egg yolk
\item \C{\half} \theme{currants}
\item \C{\quarter} candied peel, chopped 
\end{ingredients}

\begin{directions}
\item Combine water, \Tp{1} sugar and yeast.
\item Let stand 10~minutes.
\item In a separate bowl, blend together remaining sugar, flour, cinnamon, nutmeg, salt and cloves.
\item In a separate bowl, whisk together milk, butter, egg and egg yolk.
\item Form a well in dry ingredients and add liquid mixtures.
\item Stir until a soft dough forms.
\item Turn out and knead for 8~minutes.
\item Place in a greased bowl and let rise until doubled in bulk. Approximately 1~hour.
\item Punch down and knead in currants and peel.
\item Shape into a \cm{30} log and cut into 9~pieces.
\item Stretch and round each piece into a seamless ball.
\item Place \cm{5} apart on a greased pan.
\item Cover and let rise for 35~minutes.
\item Bake buns in a \tF{400} oven for 16~minutes.
\end{directions}

\subrecipe{Glaze}
\begin{ingredients}
\item \Tp{2} water
\item \Tp{2} sugar
\end{ingredients}

\begin{directions}
\item In a saucepan, dissolve sugar in water over medium heat.
\item Brush over buns.
\item Let cool.
\end{directions}

\subrecipe{Icing}
\begin{ingredients}
\item \C{\half} sugar
\item \tp{2} water
\end{ingredients}

\begin{directions}
\item Stir ingredients together.
\item Using a piping bag, create a cross on the top of each bun.
\end{directions}

\end{recipe}
