\begin{recipe}{Pett'le\FIXME}{Diego Di Lorenzo}{}

\begin{ingredients}
\item \kgr{1} fine semolina flour
\item \gr{25} compressed yeast
\item \gr{25} salt
\item \gr{100} sourdough starter~(optional)
\item \gr{r6700}\FIXME{} water, warm
\item oil or lard for frying
\end{ingredients}

\begin{directions}
\item Dissolve yeast in some water to form a slurry.
\item Dissolve salt in some water.
\item Combine yeast mixture and salt mixture in a mixture.
\item Begin to knead dough.
\item Slowly add flour and water alternately.
\item Knead until dough pulls away from the sides of the bowl. Increase speed beyond recommended speed for dough. The dough should have the consistency of pancake batter. It must be very well developed.
\item Sprinkle the surface of the dough with flour and cover with a tea towel.
\item Let rise until bulk increases by half. Approximately \threequarter{}~hours.
\item Turn out onto a floured tea towel and fold tea towel to form a packet.
\item Let rise until packet is elastic. Approximately \half{}~hour.
\item Heat oil to \tC{200} in a roaster.
\item Cut strips \inch{6} long and \inch{\threequarter} in diameter.
\item Form into rings.
\item Drop into hot oil.
\item Use the handle of a wooden spoon to swirl the centre of the ring to enlarge the pett'le.
\item Flip over when the underside is pale golden.
\item Remove when both sides are pale golden.
\item Let stand in a bowl with paper towel at the bottom.
\item Serve with granulated sugar for dipping.
\end{directions}
\method{Bread}

\end{recipe}
