\begin{recipe}{Cabbage Rolls}{Baba}{}

\begin{ingredients}
\item 3 to 4~medium \theme{cabbage}s
\item 1~bottle of tomato cocktail~(V8 preferred)
\item \lbs{2} \theme{rice}
\item bouillon cube~(optional)
\item \lbs{\quarter} to \lbs{\half} butter
\item \lbs{2} ground \theme{veal} or \theme{beef}
\item 2 to 3~onions, chopped
\item 2~cloves of garlic, minced
\item 2~eggs, beaten
\item salt
\item pepper
\item \C{1} water
\item shortening or oil
\end{ingredients}

\begin{directions}
\item Rinse rice with hot water.
\item Cook rice in salted water with bouillon cube until almost done.
\item Separately, cook onions in butter until soft but without colour.
\item Add garlic to onion mixture and cook a few minutes more.
\item Mix onion mixture, rice, and veal.
\item Season with salt, and pepper.
\item Add eggs to rice mixture and mix in evenly.
\item Steam cabbage in salted water, or, if very fresh, water with vinegar.
\item Remove cabbage leaves as they become flexible. Do not overcook.
\item Rinse leaves in cold water immediately.
\item Preheat oven to \tF{375}.
\item Grease bottom and sides of a roaster with shortening.
\item Line with foil.
\item Pour water underneath the foil.
\item Roll rice in small full or large half leaves, cutting away hard centre vein if present.
\item Line roaster with unusable leaves.
\item Stand rolls in roaster, salting each complete row.
\item When roaster is full, pour tomato cocktail over rolls until almost at top of roaster. Leave head space to avoid boil-over.
\item Cover with another layer of unusable leaves, then foil.
\item Bake for \half~hour.
\item Reduce temperature to \tF{350} and cook until done. Approximately 3~hours. During cooking, replenish room-temperature tomato cocktail if necessary.
\end{directions}

\hint{Veal is raw when added to rice.}
\end{recipe}
