\begin{recipe}{Apple Streusel Cake}{Creative Cook's Kitchen}{12~servings}

Streusel
\begin{ingredients}
\item \C{1} light brown sugar
\item \C{1} \theme{apple}s, chopped
\item \C{1} \shtheme{almond}{nuts}s, \shtheme{pecan}{nuts}s, or \shtheme{walnut}{nuts}s, sliced~(optional)
\item \C{\quarter} all-purpose flour
\item \tp{1} cinnamon
\item \Tp{3} butter, melted
\end{ingredients}

Batter
\begin{ingredients}
\item \C{1} all-purpose flour
\item \tp{1} baking powder
\item \tp{1} baking soda
\item \C{\half} butter, softened
\item \C{\half} sugar
\item 3~eggs
\item \tp{\half} vanilla
\item \C{\third} orange juice
\end{ingredients}

Glaze
\begin{ingredients}
\item \C{\half} confectioner's sugar
\item \tp{2\half} orange juice
\end{ingredients}

\begin{directions}
\item Preheat oven to \tF{350}.
\item Combine all streusel ingredients except butter.
\item Stir in melted butter.
\item Separately combine flour, baking powder, and baking soda for batter.
\item Beat butter and sugar until light and fluffy.
\item Add eggs, beating after each addition.
\item Add vanilla.
\item Add alternately flour mixture and orange juice into egg mixture.
\item Spoon half the batter into a tube pan.
\item Spoon remaining batter into pan.
\item Swirl batter with a knife to create a marble pattern.
\item Bake for 15~minutes.
\item Sprinkle with remaining streusel.
\item Bake for 30 to 35~minutes.
\item Let cool completely.
\item Combine confectioner's sugar and orange juice for glaze.
\item Drizzle over cake.
\end{directions}
\method{Creaming}
\end{recipe}
