\begin{recipe}{Cheesecake Supreme}{}{}

Crust
\begin{ingredients}
\item \C{1} flour
\item \C{\quarter} sugar
\item \tp{1} lemon zest
\item \C{\half} butter
\item 1~egg yolk, beaten
\item \tp{\quarter} vanilla
\end{ingredients}

Filling
\begin{ingredients}
\item \oz{40} \htheme{cream}{cheese}
\item \tp{\quarter} vanilla
\item \tp{\threequarter} lemon zest
\item \C{1\third} sugar
\item \Tp{3} flour
\item \tp{\quarter} salt
\item \C{1} eggs~(approximately 4 to 5)
\item 2~egg yolks
\item \C{\quarter} whipping \theme{cream}
\end{ingredients}

Glaze
\begin{ingredients}
\item 2 to \C{3} fresh berries
\item \C{1} water
\item \tp{1\half} cornstarch
\item \half{} to \C{\threequarter} sugar~(depending on sweetness of berries)
\end{ingredients}

\begin{directions}
\item Preheat oven to \tF{400}.
\item Prepare crust by combining flour, sugar, and lemon peel.
\item Cut in butter.
\item Add egg yolk and vanilla.
\item Pat half the dough into a spring-form pan.
\item Bake for 8~minutes.
\item Preheat oven to \tF{450}.
\item Let cool.
\item Pat remainder up the sides approximately \inch{1\half}.
\item Prepare filling by combining cream cheese, vanilla, and zest.
\item Separately, combine sugar, flour, salt, eggs, and egg yolks.
\item Slowly blend egg mixture into cheese mixture.
\item Mix in whipping cream.
\item Pour into pan.
\item Bake for 12~minutes.
\item Reduce heat to \tF{300}.
\item Bake for 55~minutes.
\item Crush \C{1} berries.
\item Place remaining berries on top of the cake.
\item Add water to crushed berries.
\item Cook for 2 to 3~minutes.
\item Strain berries.
\item Mix cornstarch and sugar.
\item Stir mixture into berry juice.
\item Bring to a boil, stirring constantly.
\item Cook until thick.
\item Pour over cake.
\end{directions}

\end{recipe}
