\begin{recipe}{Pumpkin Streusel Coffee Cake}{Canadian Living}{10~servings}

\begin{ingredients}
\item \C{1\half} all-purpose flour
\item \tp{1} baking soda
\item \tp{2} baking powder
\item \tp{1\half} pumpkin pie spice
\item \tp{1} cinnamon
\item \tp{\half} salt
\item \tp{\quarter} nutmeg
\item \C{\half} butter, softened
\item \C{1} sugar
\item 2~eggs
\item \C{1} \theme{pumpkin} pur\'ee
\item \C{\half} sour cream
\end{ingredients}

\begin{directions}
\item Preheat oven to \tF{350}.
\item Grease and line a \inch{9} spring-form pan.
\item In a bowl, whisk together dry ingredients; divide in thirds.
\item Cream butter and sugar.
\item Add eggs on at a time to creamed mixture.
\item Add pumpkin to creamed mixture.
\item Stir in a third of dry ingredients.
\item Alternately stir in half of sour cream, then dry ingredients.
\item Pour into pan, smoothing top.
\item Pour streusel on top.
\item Bake 55 to 60~minutes.
\item Cook 15~minutes.
\item Release from pan.
\item Allow to cool.
\item Drizzle glaze over cake.
\end{directions}


\subrecipe{Streusel}
\begin{ingredients}
\item \C{\threequarter} all-purpose flour
\item \C{\quarter} light brown sugar
\item \C{\quarter} sugar
\item \tp{\quarter} salt
\item \C{\quarter} butter, melted
\end{ingredients}

\begin{directions}
\item Mix all ingredients except butter.
\item Using a fork, mix in butter until moistened.
\end{directions}

\subrecipe{Glaze}
\begin{ingredients}
\item \C{\threequarter} confectioner's sugar
\item \Tp{1} milk or cream
\end{ingredients}

\begin{directions}
\item Combine all ingredients.
\end{directions}

\end{recipe}
