\begin{recipe}{Tea Ring\FIXME}{Curtin Publicators}{12~servings}

\begin{ingredients}
\item \C{\twothird} milk, scalded
\item \C{\quarter} butter
\item \C{\quarter} sugar
\item \tp{\half} salt
\item \tp{2\quarter} dry active yeast
\item 1~egg
\item 2\half{} to \C{3} flour
\item \Tp{2} butter, softened
\item \C{\half} brown sugar
\item \tp{1} cinnamon
\item \tp{2} lemon zest
\item ??? \shtheme{walnut}{nuts}s
\item \C{\half} \theme{raisins}
\item \C{\half} confectioner's sugar
\item \Tp{2} milk
\item \Tp{3} \shtheme{almond}{nuts}s, sliced
\item \tp{\half} almond extract
\end{ingredients}

\begin{directions}
\item Add \C{quarter} butter, sugar, and salt to scalded milk.
\item Let cool until lukewarm.
\item Dissolve yeast in scalded milk.
\item Add egg and half of the flour.
\item Beat until smooth.
\item Slowly add remaining flour until dough is easy to handle.
\item Knead dough until smooth and elastic. Approximately 5~minutes.
\item Place in a greased bowl and let rise until doubled in bulk.
\item Punch down and roll out to a \inch{15}$\times$\inch{10} rectangle.
\item Spread with butter.
\item Mix brown sugar, cinnamon, zest, raisins, and walnuts.
\item Spread evenly over surface of dough.
\item Roll up, beginning at the wide side, and seal seam.
\item Shape into a ring on a baking sheet.
\item Cut slits \twothird{} of the way down at \inch{1} interval.
\item Turn each slice on its side.
\item Cover and let rise until doubled in bulk.
\item Preheat oven to \tF{350}.
\item Bake until browned. Approximately 25 to 30~minutes.
\item Combine confectioner's sugar, milk, and almond extract.
\item Frost cake, while warm, with milk mixture.
\item Sprinkle with almonds.
\end{directions}

\end{recipe}
