\begin{recipe}{Challah}{Mike Avery\FIXME}{1~loaf}

\begin{ingredients}
\item \C{1} starter
\item \C{\half} water
\item \C{3\twothird} all-purpose flour
\item \tp{2} salt
\item \C{\quarter} sugar
\item \C{\quarter} oil
\item 1~egg, lightly beaten
\item 2~egg yolks, lightly beaten
\item egg wash
\item poppy or sesame seeds
\end{ingredients}

\begin{directions}
\item Mix the starter, egg, egg yolks, sugar, oil, \half{} of the flour, and the salt. 
\item Add more flour, a bit at a time, until the dough is too thick to stir.
\item Pour out the dough onto a lightly floured surface.
\item Knead the dough, adding more flour sparingly, until the dough is smooth, satiny, has lost most of its stickiness, and is fairly firm. You probably should not use all the flour called for above.
\item Cover and allow to rise until tripled in volume.
\item Punch down the dough and knead briefly
\item Cut into four pieces of the same weight. Divide one piece into three pieces of the same weight.
\item Form all the balls into strands of about 12 to 14 inches in length, tapered so the centre of each piece is thicker than the ends.
\item Braid the three thick strands into a loaf and set aside.
\item Braid the three smaller strands into a smaller loaf.
\item Lightly indent the top centre of the larger loaf down its length.
\item Wet it slightly with water and put the smaller loaf on top of the indention.
\item Brush this egg wash all over the nested loaves.
\item Let rise until doubled.
\item Preheat oven to \tF{350}.
\item When the oven is ready, brush the loaves with the egg wash again.
\item Sprinkle the loaves with poppy or sesame seeds.
\item Bake approximately 35~minutes. If there is a white line between the braids, continue baking until it disappears. If loaf is browning too much, cover it with parchment tent.
\end{directions}

\end{recipe}
