\begin{recipe}{Pandoro}{}{2~loaves}

This recipe is extremely complicated and it requires a special pan. Proofing must be done in a proofer at \tC{30}.

\subrecipe{Evening 5~days Before Baking}
\begin{ingredients}
\item \gr{15} malt extract
\item \gr{10} Epsom salts
\item \gr{125} water
\end{ingredients}

\begin{directions}
\item Combine all ingredients and a magnetic bead in a vented \mL{250} Erlenmeyer flask.
\item Boil flask in a covered water bath for 45~minutes.
\item Chill to room temperature.
\item Inoculate flask with frozen stock of osmotolerant yeast.
\item Gently mix on a magnetic stirrer at room temperature.
\end{directions}

\subrecipe{Evening 2~days Before Baking}
Refresh the starter.

\subrecipe{11:00 the Day Before Baking}
\begin{ingredients}
\item \gr{30} starter
\item \gr{20} water
\item \gr{54} flour
\end{ingredients}

\begin{directions}
\item Combine all ingredients.
\item Knead until smooth. The dough is very stiff.
\item Proof.
\end{directions}

Also:

\begin{directions}
\item Decant yeast mixture into a tall narrow tube.
\item Chill.
\end{directions}

\subrecipe{15:00 the Day Before Baking}
\begin{ingredients}
\item \gr{15} water
\item \gr{115} flour
\item 1~egg
\item \gr{30} granulated sugar
\end{ingredients}

\begin{directions}
\item Decant the liquid from the tube taking care not to disturb the sediment at the bottom.
\item Add water.
\item Swirl to dissolve yeast sediment at bottom of tube.
\item Add flour to a mixing bowl.
\item Tear previous mixture into chunks and drop in the bowl.
\item Add yeast liquid and egg.
\item Stir until a stiff dough forms.
\item Knead very stiff dough until smooth.
\item Gradually knead in sugar.
\item Proof until quadrupled in bulk.
\end{directions}

\subrecipe{19:00 the Day Before Baking}
\begin{ingredients}
\item \gr{30} cocoa butter, melted~(optional)
\item \gr{200} unsalted European-style butter, room temperature
\item \gr{225} flour
\item \gr{5} salt
\item \gr{10} honey
\item 4~eggs
\item \gr{15} vanilla (or substitute water)
\item 2~egg yolks
\item \gr{135} sugar
\end{ingredients}

\begin{directions}
\item Whip the butter.
\item Add cocoa butter while whipping.
\item Whip until whitish and doubled in volume.
\item Set butter aside.
\item Butter and flour two \C{8} pans.
\item Combine flour and salt in the work bowl.
\item Tear previous mixture into chunks and drop in the work bowl.
\item Add honey and 3~eggs.
\item Mix with a dough hook until the dough cleans the sides of the bowl.
\item Switch to the paddle.
\item Add remaining egg and mix until smooth, gradually increasing speed to medium. The dough should cling to the bowl.
\item Reduce speed to low.
\item Add vanilla and mix until smooth, increasing speed.
\item Reduce speed to low.
\item Add 1~egg yolk and mix until smooth, increasing speed.
\item Repeat with remaining yolk.
\item Reduce speed to low.
\item Add \half{} the sugar and mix until smooth, increasing speed.
\item Repeat with remaining sugar.
\item Reduce speed to low.
\item Add \half{} the whipped butter and mix until smooth, increasing speed.
\item Repeat with remaining butter.
\item Mix until smooth and silky.
\item Divide the dough in half and place each half in a pan.
\item Proof.
\end{directions}

\subrecipe{8:30 Baking Day}
\begin{directions}
\item Preheat oven to \tF{350}.
\item Bake for 30 to 35~minutes. Rotating pans half way through baking.
\item Let cool for 30~minutes.
\item Invert and release from pans.
\item Let cool completely.
\item Dust with confectioner's sugar.
\end{directions}

\hint{These keep extremely well if kept in an air-tight container or bag. They can typically keep for a month at room temperature.}
\hint{The pans are extremely difficult to find. They need to be \C{8}. Any tall narrow pan should work.}
\hint{\seerecipe{Osmotolerant} can be made from regular yeast, if the instant form is not available commercially.}
\end{recipe}
