\begin{recipe}{Pennsylvania Dutch Hard Pretzels}{}{25}

\begin{ingredients}
\item \gr{88} sourdough starter
\item \gr{8} salt
\item \gr{5} malt powder or malt syrup
\item \gr{60} oil
\item \gr{160} water
\item \gr{202} all-purpose flour
\item \gr{150} cake flour
\item \gr{15} per \L{1} lye
\item coarse salt~(ideally, pretzel salt)
\end{ingredients}

\begin{directions}
\item Combine starter, salt, malt, water, and flour and knead until smooth and elastic.
\item Let rise for 8~hours.
\item Divide into \gr{25} pieces and round.
\item Let rest 30~minutes.
\item On a lightly floured surface, roll each piece into a rope that is \inch{\half} in the middle third and \inch{\quarter} for third nearest each end. If the rope is too thick, the pretzel will not dry during baking and will be tough.
\item Twist each rope by rolling the ends in opposite directions, then shape each rope into a pretzel shape, and lay on a couche. The thinner ends of the rope should mean that the main backbone of the pretzel and the middle are approximately the same diameter. Make sure there is plenty of space in the holes of each pretzel. If they close up during rising, they will not dry duing baking.
\item Let rise for 3 to 4~hours, until slightly puffed. Intentionally underproof, like a baguette.
\item Preheat oven to \tF{550}.
\item Fill a stainless steel pot with water. It does not need to be very deep, but deep enough to get a spoon under a submerged pretzel.
\item While wearing rubber gloves, add lye to water. Alwayas add lye to water; never water to lye.
\item Heat lye mixture until all lye dissolves and mixture is very hot. It does not need to come to a boil.
\item On a sheet pan, place an inverted wire cooling rack. Spray rack with non-stick cooking spray. Liberally salt the sheet pan.
\item Working in batches, place pretzels in the lye path for 5~seconds, then transfer to the tray. Do not let pretzels sit; they must get in the oven quickly. Boiling and baking batches should be the same. Do not boil the next batch until the oven is free.
\item Using a knife or razor, slash the ``belly'' of each pretzel
\item Sprinkle coarse salt on top of the pretzels.
\item Lift the entire wire rack off of the pan and bake for 10~minutes on a pizza stone.
\item Remove from the oven and peel pretzels off of the rack.
\item Put pretzels in a dehydrator at \tC{70} for 24~hours.
\item Dry for 13~hours until pretzels are hard when pressed firmly.
\end{directions}

\hint{This recipe is a hybrid of information from tours of Martin's and Hammond's pretzel factories.}
\hint{If making multiple batchs, keep the oven at \tF{550} and do the 10~minute bake for all batches, then reduce temperature and perform the second bake. It is not a problem if the pretzels cool between bakes.}
\end{recipe}
